A Simple Model of Energy Transition Under a Carbon Budget

### 2015-04-27 DraftApril2715.tex
table done

\begin{table}[h]\label{tab:ParamValues}
\begin{tabulary}{1.0\textwidth}{LLLL}
Variable & Description & Value\\
\hline
$\alpha$ &  \% Business As Usual Emissions  &  Varied \\
$Fl_min$ & Minimum kWh/year per dollar - Clean Capital & \\
$F_max$ & Maximum kWh/year per dollar - Clean Capital & \\
$Scale$ & Transition Speed  (Scale of Logistic Function) & \\
$Fh_min$ & Minimum kWh/year per dollar - Dirty Capital & \\
$Fh_max$ & Maximum kWh/year per dollar - Dirty Capital & \\
$G_0$ & Base energy demand (bn kWh/year) & \\
$G_m$ & Annual increase in energy demand (bn kWh/year) & \\
$c^l$ & Capacity Factor Clean Capital & 30\% \\
$c^h$ & Capacity Factor Dirty Capital & 50\% \\
\hline
\end{tabulary}
\caption{Key parameters of simulation. Note that energy demand is excluding the generating capacity of hydroelectric dams and nuclear plants}
\end{table}

@@

@@

\bibitem{JR2006}
to do in papers file

@@

\bibitem{Jacobson}
to do in papers file

\bibitem{NEMS}
to do in papers file

>>>>

\begin{table}[h]\label{tab:ParamValues}
\begin{tabulary}{1.0\textwidth}{LLLL}
Variable & Description & Value\\
\hline
$\alpha$ &  \% Business As Usual Emissions  &  Varied \\
$Fl_min$ & Minimum kWh/year per dollar - Clean Capital & 0.343349882\\
$F_max$ & Maximum kWh/year per dollar - Clean Capital & 2.8658669 \\
$Scale$ & Transition Speed  (Scale of Logistic Function) & Varied \\
$Fh_min$ & Minimum kWh/year per dollar - Dirty Capital & 2.628 \\
$Fh_max$ & Maximum kWh/year per dollar - Dirty Capital & 4.7764449 \\
$G_0$ & Base energy demand (bn kWh/year) & 2798.5 * 10**9 bn kWh\\
$G_m$ & Annual increase in energy demand (bn kWh/year) & 32.238 * 10**9 bn kWh \\
$c^l$ & Capacity Factor Clean Capital & 30\% \\
$c^h$ & Capacity Factor Dirty Capital & 50\% \\
\hline
\end{tabulary}
\caption{Key parameters of simulation. Note that energy demand is excluding the generating capacity of hydroelectric dams and nuclear plants}
\end{table}

@@

\bibitem{Jacobson}
MZ Jacobson, MA Delucchi. Providing all global energy with wind, water, and solar power, Part I: Technologies, energy resources, quantities and areas of infrastructure, and materials. Energy Policy 39 (2011) 1154?1169

\bibitem{NEMS}
Energy Information Administration. The National Energy Modeling System: An Overview. October 2009

\bibitem{JR2006}
Jaccard and Rivers, Heterogeneous capital stocks and the optimal timing for CO2 abatement. Resource and Energy Economics 29 (2007) 1?16.

@@

@@
